A Study on Neural Models for Target-Based Computer-Assisted Musical Orchestration

### 2020-10-09 paper/aimusic2020/paper.tex
Add explanation of terms in eqn 1
Minor fixes

For a given number of instruments $N$, each input to our model is a combination of $N$ TinySOL samples chosen among an orchestra of 10 instruments. The data is generated by selecting $N$ random TinySOL samples, leading to a variety of instruments, pitches, and dynamics; we did not allow the same instrument to be chosen more than three times in order to ensure variety in the mixtures. Then the chosen samples are combined to be played simultaneously and normalized by the number of instruments. The resulting combination has a sample rate of $44100$Hz and is padded or trimmed to be exactly 4 seconds long. The Mel spectrogram of the mixture is computed using an FFT hop length of 2048 samples (the window of each FFT is $46$ms wide) and a 128 Mel bins. Therefore, the Mel features fed to the model are matrices of size $128\times 345$.

@@

For quantitative evaluation, we used the distance metric defined in Eqn. \ref{distance} to calculate differences in timbre between targets and solutions. This metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization.

>>>>

For a given number of instruments $N$, each input to our model is a combination of $N$ TinySOL samples chosen among an orchestra of 10 instruments. The data is generated by selecting $N$ random TinySOL samples, leading to a variety of instruments, pitches, and dynamics; we did not allow the same instrument to be chosen more than three times in order to ensure variety in the mixtures. Then the chosen samples are combined to be played simultaneously and normalized by the number of instruments. The resulting combination has a sample rate of $44100$Hz and is padded or trimmed to be exactly 4 seconds long. The Mel spectrogram of the mixture is computed using an FFT hop length of 2048 samples (the window of each FFT is $46$ms wide) and 128 Mel bins. Therefore, the Mel features fed to the model are matrices of size $128\times 345$.

@@

For quantitative evaluation, we used the distance metric defined in Eqn. \ref{distance} to calculate differences in timbre between targets and solutions. This metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization. The equation takes in the full FFT of the target $x$ and full FFT of the solution $\tilde{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways.
